Empirical Modeling Constraints on the Galaxy Size-Halo Connection

### 2017-10-02 paper/galsize_paper.tex
Updated figures with correct axis labels

\title[The Emergent Simplicity of Galaxy Size]
{The Emergent Simplicity of Galaxy Size}

@@

>>>>

\title[On the Galaxy Size-Halo Connection]
{Empirical Modeling Constraints on the Galaxy Size-Halo Connection}

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/rs_correlation_visual.pdf}
\caption{
{\bf Illustration of galaxy \& halo profile co-evolution.}
}
\label{fig:coevolution}
\end{figure}
%-----------------------------------------------------------------------------------------------------
